|

### 2024-08-09 doc/paper.qmd
update paper.qmd

---
title: |
  | Earnings Management and Investor Protection:
  | Accounting Reading Group - Assignment III\vspace{1cm}
author:
  - name: Melisa Mazaeva
    email: melisa.mazaeva@student.hu-berlin.de
    affiliations:
      - Humboldt-Universität zu Berlin  
date: today
date-format: MMM D, YYYY [\vspace{1cm}]
abstract: |
  | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide an infrastructure for open science-oriented empirical projects. Leveraging external Worldscope data sets on financial data, the repository showcases a reproducible workflow that integrates Python scripts for data analysis. The project’s output demonstrates a comprehensive application of skills to replicate and extend the findings from the seminal paper by Leuz, Nanda, and Wysocki (2003), particularly in providing descriptive statistics for the four individual earnings management measures as well as the aggregate earnings management score across various countries. In doing so, it documents and discusses the research design choices made and the variations between the original and reproduced results. This code base, adapted from TREAT, should give you an overview on how the template is supposed to be used for my specific project and how to structure a reproducible empirical project.
  | \vspace{6cm}
bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: false
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
number-sections: true 
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}  # Added this line to ensure the first paragraph is indented for better readability
  - \usepackage[margin=1in]{geometry}
---

@@

The following paper illustrates how to use open science tools in empirical accounting research.

The original study by @Leuz_2003 examines systematic differences in earnings management (EM) across 31 countries and proposes that these differences are influenced by the level of investor protection. Specifically, they argue that stronger investor protection reduces earnings management by limiting insiders’ ability to acquire private control benefits.

This paper presents details on a replication of Table 2 Panel A from the seminal paper by @Leuz_2003. The original table provides descriptive statistics for four individual earnings management measures and the aggregate earnings management score across various countries, highlighting significant differences in EM practices between Continental Europe, Asia, and Anglo-American countries.

@@

The analysis includes pulling and filtering the relevant financial data, identifying relevant companies and countries based on the authors’ requirements, calculating the earnings management measures for each country, and examining the relationship between each country’s aggregate earnings management score and its ranking based on made explicit assumptions whenever the paper is not clear on how to proceed.

## delete. from mine
Note that intermediate check steps have been omitted for brevity. The full code, including intermediate print steps to verify outputs, is presented in `code/python/Assignment1_analyze_residual_income.py`.

@@

print(prep_latex_table(
    results['table_1'],
    caption='Number of Firm-Year Observations per Country',
    label='tab:table_1'
))
```

>>>>

---
title: |
  | Earnings Management and Investor Protection:
  | Accounting Reading Group - Assignment III\vspace{1cm}
author:
  - name: Melisa Mazaeva
    email: melisa.mazaeva@student.hu-berlin.de
    affiliations:
      - Humboldt-Universität zu Berlin  
date: today
date-format: MMM D, YYYY [\vspace{1cm}]
abstract: |
  | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide an infrastructure for open science-oriented empirical projects. Leveraging external Worldscope data sets on financial data, the repository showcases a reproducible workflow that integrates Python scripts for data analysis. The project’s output demonstrates a comprehensive application of skills to replicate and extend the findings from the seminal paper by Leuz, Nanda, and Wysocki (2003), particularly in providing descriptive statistics for the four individual earnings management measures as well as the aggregate earnings management score across various countries. In doing so, it documents and discusses the research design choices made and the variations between the original and reproduced results. This code base, adapted from TREAT, should give you an overview on how the template is supposed to be used for this specific project and how to structure a reproducible empirical project.
  | \vspace{6cm}
bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: false
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
number-sections: true 
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}  # Added this line to ensure the first paragraph is indented for better readability
  - \usepackage[margin=1in]{geometry}
---

@@

The aim of the following paper is to illustrate how to use open science tools in empirical accounting research. The original study by @Leuz_2003 examines systematic differences in earnings management (EM) across 31 countries and proposes that these differences are influenced by the level of investor protection. Specifically, they argue that stronger investor protection reduces earnings management by limiting insiders’ ability to acquire private control benefits.

This paper presents details on a replication of Table 2 Panel A from the seminal study by @Leuz_2003. The original table provides descriptive statistics for four individual earnings management measures and the aggregate earnings management score across various countries, highlighting significant differences in EM practices between Continental Europe, Asia, and Anglo-American countries.

@@

The analysis includes pulling and filtering the relevant financial data, identifying relevant companies and countries based on the authors’ requirements, calculating the EM measures for each country, and examining the relationship between each country’s aggregate earnings management score and its ranking based on explicit assumptions made whenever the paper by @Leuz_2003 is not clear on how to proceed. The complete computation code for EM measures is available in `code/python/do_analysis.py` for detailed review if necessary. Code snippets will be presented only in exceptional cases to highlight specific points. @

@@

print(prep_latex_table(
    results['table_1'],
    caption='Replicated table - Number of Firm-Year Observations per Country',
    label='tab:table_1'
))
```
